Artistic Curve Steganography Carried by Musical Audio

### 2022-11-15 writeup/paper.tex
Tweaking experiment figures

\begin{figure}
  \centering
  \includegraphics[width=0.5\columnwidth]{2Opt.pdf}
  \caption{Every crossing in a tour can be removed with a 2-opt swap to yield a tour of a smaller distance, since, by the triangle inequality, $d(X_i, X_j) + d(X_{i+1}, X_{j+1}) < (a+d) + (b+c) = d(X_i, X_{i+1}) + d(X_j, X_{j+1})$.  This may introduce new crossings (shown in red), but these and other crossings will be resolved in future 2-opt swaps.}
  \label{fig:TwoOpt}
\end{figure}

>>>>

\begin{figure}
  \begin{minipage}[c]{0.6\textwidth}
    \caption{
      Every crossing in a tour can be removed with a 2-opt swap to yield a tour of a smaller distance, since, by the triangle inequality, $d(X_i, X_j) + d(X_{i+1}, X_{j+1}) < (a+d) + (b+c) = d(X_i, X_{i+1}) + d(X_j, X_{j+1})$.  This may introduce new crossings (shown in red), but these and other crossings will be resolved in future 2-opt swaps
    } \label{fig:TwoOpt}
  \end{minipage}
  \begin{minipage}[c]{0.38\textwidth}
    \includegraphics[width=\textwidth]{2Opt.pdf}
  \end{minipage}\hfill

\end{figure}

\begin{figure}
  \centering

  \caption{.}
  \label{}
\end{figure}
